Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-02 paper/ms.tex
update paper

\begin{figure}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Celestial positions of light curves from Sectors 6
			and 7.}  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
			Rp}<16$ target stars.
		\label{fig:lcradec}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf  Zoom of Sector 6, Camera 1 from Figure~\ref{fig:lcradec}.}
		The most populated cluster is XXX, primarily due to candidate
		members proposed by \citet{dias_proper_2014}.
		\label{fig:lcradeczoom}
	}
\end{figure}

@@

The on-sky locations of the light curves from Sectors 6 and 7
are shown in Figure~\ref{fig:lcradec}.
Black stars are the field stars for which we performed photometry,
but only to calibrate the cluster star sample.
The blue stars are the \numberlcs stars with light curves available
from \stscilink.
Most of the target stars are quite close to the galactic plane.
Gaps between CCD chips are also visible.

A zoom-in of Figure~\ref{fig:lcradec} is shown in Figure~\ref{fig:lcradeczoom}
for the Camera 1, Sector 6 field. The effects of galactic-latitude
dependent extinction are visible through the decreasing density of black
points towards the right of the image.
The highly clumped nature of the target stars is also apparent.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 6 of the \numberpcs candidate transiting planets identified
    in this studies.}
	Black points are detrended flux measurements, phased to the
	best-fit orbital period, indicated in the lower right of each panel.
	Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
	shown with blue lines.
	For display purpses, $\pm 4$ transit durations of the
	light curves are displayed.
	The vetting reports for these objects are available at XXX.	%FIXME
	The Gaia source identifiers are
	a): 5605128927705695232, 
	b): 3125263468681400320, 
	c): 5510676828723793920, 
	d): 3007171311355035136, 
	e): 5617126180115568256, 
	f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

The physical parameters quoted in Table YYY, and on exofop-TESS,
should be considered preliminary, and could be substantially improved
with an object-by-object analysis.  A few additional assumptions were
required to report some of the values.  For the stellar radii, we
assumed the $R_\star$ values and uncertainties reported in the TIC.
There were a few cases with null uncertainties in the stellar radii --
for these, we simply invented a relative uncertainty of 30\%, and note
in the comments that this was done.  There were also a few cases for
which the TIC stellar temperatures and/or radii were not available,
but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
eff}$ and $R_\star$ values, and used the stellar mass interpolated
from the \citet{pecaut_intrinsic_2013} table (assuming the star is a
dwarf) to estimate $\log g$.  The uncertainties in e.g., the planetary
radii and impact parameters were found using linear error propagation
theory, under the idealized assumption that the covariance between all
stellar and planetary parameters was zero.

Finally, to determine the names of the objects -- and whether they
had already been identified as TOIs or cTOIs -- we cross-referenced
based on a combination of the TIC identifier, spatial position, and
the ephemeris of each object.

>>>>

\begin{figure*}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Positions of light curves from Sectors 6
			and 7 in galactic coordinates.}
		    Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$ target stars.
		\label{fig:lcgalactic}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf  Zoom and coordinate transformation
			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
		The most populated cluster is XXX, primarily due to candidate
		members proposed by \citet{dias_proper_2014}.
		\label{fig:lcradeczoom}
	}
\end{figure}

@@

The on-sky locations of the light curves from Sectors 6 and 7
are shown in Figure~\ref{fig:lcgalactic}.
Black stars are the field stars for which we performed photometry,
but only to calibrate the cluster star sample.
The blue stars are the \numberlcs stars with light curves available
from \stscilink.
Most of the target stars are quite close to the galactic plane.
Gaps between CCD chips are also visible.

A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
for the Camera 1, Sector 6 field. The effects of galactic-latitude
dependent extinction are visible through the decreasing density of black
points towards the right of the image.
The highly clumped nature of the target stars is also apparent.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Six of the \numberpcs candidate transiting planets identified
    from this work.}
    Black points are detrended flux measurements, phased to the
    best-fit orbital period, indicated in the lower right of each panel.
    Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
    shown with blue lines.
    For display purpses, a window of $\pm 4$ transit durations from the
    mid-point is displayed.
    The vetting reports for these objects are available at XXX.	%FIXME
    % TODO: include age? T mag?
    The Gaia source identifiers are
    a): 5605128927705695232, 
    b): 3125263468681400320, 
    c): 5510676828723793920, 
    d): 3007171311355035136, 
    e): 5617126180115568256, 
    f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

The physical parameters quoted in Table YYY, and on exofop-TESS,
should be considered preliminary, and could be substantially improved
with an object-by-object analysis.  A few additional assumptions were
required to report some of the values.  For the stellar radii, we
assumed the $R_\star$ values and uncertainties reported in the TIC.
There were a few cases with null uncertainties in the stellar radii --
for these, we simply invented a relative uncertainty of 30\%, and note
in the comments that this was done.  There were also a few cases for
which the TIC stellar temperatures and/or radii were not available,
but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
eff}$ and $R_\star$ values \citep{andrae_apsis_2018}, and a stellar
mass interpolated from the \citet{pecaut_intrinsic_2013} table
(assuming the star is a dwarf) to estimate $\log g$.  The
uncertainties in e.g., the planetary radii and impact parameters were
found using linear error propagation theory, under the idealized
assumption that the covariance between all stellar and planetary
parameters was zero.

Finally, to assign the names of the planet candidates -- and determine
whether they had already been identified as TOIs or cTOIs -- we used
lists downloaded from the \url{tev.mit.edu} alert site for TOIs, and
from \url{exofop.ipac.caltech.edu/tess} for cTOIs.  We
cross-referenced based on a combination of the TIC identifier, spatial
position, and the ephemeris of each object.
